% Chapter Template

\chapter{Extending the Analysis} % Main chapter title

\label{Chapter6} % Change X to a consecutive number; for referencing this chapter elsewhere, use \ref{ChapterX}

\lhead{Chapter 6. \emph{Extending the Analysis}} % Change X to a consecutive number; this is for the header on each page - perhaps a shortened title

The present system focuses on only two companies, competing over a single attribute of the agent. It is limited to a specific  part of a very wide spectra of possibilities.

In future, there are possibilities to extend this sytem and anlyse a diversity of scenarios.

%----------------------------------------------------------------------------------------
%	SECTION 1
%----------------------------------------------------------------------------------------

\section{Extending the analysis to more companies}

The environment could always include more companies competing for the same slot. This might provide valuable insight, specially for cases where two companies might collaborate for mutual benefit against a common competing company.

%----------------------------------------------------------------------------------------
%	SECTION 2
%----------------------------------------------------------------------------------------

\section{Extending the analysis to more attributes}

The companies in the present model only compete for a single attribute, but this may be extended to make them compete for multiple attributes of the  agents. However, this will significantly increase the complexity if the model.

%----------------------------------------------------------------------------------------
%	SECTION 3
%----------------------------------------------------------------------------------------

\section{Extending the analysis to collaborative diffusion over single attribute or multiple attributes}

While the presented system only lets the companies compete against each other, it might be interesting to see how they behave when they are collaborating towards a common goal. This could be done for a single attribute as well as for multiple attributes. 
%----------------------------------------------------------------------------------------
%	SECTION 4
%----------------------------------------------------------------------------------------

\section{Extending to Other Systems}

The present system is targeted towards company policies, but the generic nature and social structure of the model imparts flexibility to the system, which makes it easy to extend to other systems as well.